Weakly informative observations: identifying the weakest player

### 2019-11-18 inst/loser.Rmd
minor rewording

The likelihood can be shown to be $\frac{1}{n}$ (which is clear on
intuitive grounds: $H_3$ says that all players are equivalent and if
this is correct, then one would identify players `a` as the worst with
a probability of $\frac{1}{n}$).  Note again that this is loose
language as likelihood is only defined up to a multiplicative
constant.

@@

We are now in a position to define a likelihood function for
$H-1,H_2,H_3$:

@@

(recall that $n$ is the number of competitors).  We can see that the
likelihood ratio ${\mathcal L}(H_2)/{\mathcal L}(H_1)$ is 0.5 for an
observation that I come last.  This is exactly the same as the
likelihood ratio for the following situation: we toss a coin which is
either fair ($H_\mbox{fair}$) or two-headed ($H_\mbox{2heads}$).  We
observe a head.  Then ${\mathcal L}(H_\mbox{2heads})/{\mathcal
L}(H_\mbox{fair}) = 0.5$ as well (this is Edwards's valet and black
and white ball thought experiment).

>>>>

The likelihood can be shown to be $\frac{1}{n}$ (which is clear on
intuitive grounds: $H_3$ says that all players are equivalent and the
order statistic is totally random.  If this is correct, then one would
identify player `a` as the worst with a probability $\frac{1}{n}$).
Note again that this is loose language as likelihood is only defined
up to a multiplicative constant.

@@

We are now in a position to define a likelihood function on the three
hypotheses $H_1,H_2,H_3$:

@@

(recall that $n$ is the number of competitors).  We can see that the
likelihood ratio ${\mathcal L}(H_2)/{\mathcal L}(H_1)$ is 0.5 for an
observation that competitor `a` comes last.  This is exactly the same
as the likelihood ratio for the following situation: we toss a coin
which is either fair ($H_\mbox{fair}$) or two-headed
($H_\mbox{2heads}$).  We observe a head.  Then ${\mathcal
L}(H_\mbox{2heads})/{\mathcal L}(H_\mbox{fair}) = 0.5$ as well (this
is Edwards's valet and black and white ball thought experiment).
